---
title: GBADS - Livestock Value 
output: 
        github_document:
            toc: true 
bibliography: references.bib
nocite: '@*'
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/chicago-fullnote-bibliography.csl
link-citations: yes
suppress-bibliography: false
html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
library(here)
library(knitr)
``` 

```{r, echo = FALSE, results='asis'}
cat(
  badge_license("CC BY-SA 4.0"),
  badge_lifecycle("experimental")
)
```



# Description
 
This repository contains all `R` code and output data for the [*GBADS*](https://animalhealthmetrics.org/) Global Livestock 
value estimation manuscript.  
This manuscript attempts to produce an estimate of the total economic value 
of farmed livestock and aquaculture based on [*FAOSTAT*](https://www.fao.org/faostat/en/) production data. 
 
 
# Repository Structure 

This repository is structured similar to an R package, however, there are 
minimal differences which make this package non-conforming to certain standards. 

## Make

The `R` directory contains any common functions which are used across the entire
project. The `inst` directory contains `R` scripts which are intended to be 
run via the GNU `Makefile` which specifies the required processes to build 
each target. 
Targets are run using the syntax 

```
$ make name-of-file-to-make
```

Project locations and directory structure are outlined in the project 
configuration file `conf/config.yml`, in accessing these parameters in code 
 is managed by the `R` package `config`.
 
Environment and package management is done using `renv`, `renv.lock` specifies the 
hashes for each package used.  Package imports are also listed in the 
package `DESCRIPTION` file. 

## Data 

Currently the processed and output data is located in `data/processed/` and 
`data/output`. Source data is located in `data/source` and is not 
included in this repository due to its size. Data was originally 
tracked using [***DVC***](https://dvc.org/) but has been removed due to 
issues with the cloud storage configuration. 
Output data is primarily stored in `parquet` files. 

## Figures and Tables 

Output figures and tables are located in `output/figures/`, `output/tables/`. 

*(Note: This is specified in the project configuration yaml file)*

## Codes 

FAOSTAT item codes and country codes are located in `data/codes`. 

*(Note: This is specified in the project configuration yaml file)*

## Methods Documentation

Supplementary methods documentation is located in the 
package `vignettes` directory. 

 
 
# Licence 
 
 This project is under a creative commons licence. 


# R Package References

```{r, echo=FALSE, include=FALSE, message=FALSE, error=FALSE, warning=FALSE}
# Attach all packages in lockfile
sapply(unique(renv::dependencies()$Package),
  require,
  character.only = TRUE
)
```


```{r, results='asis', echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
report::cite_packages(sessionInfo())
```

# References
