---
title: "GBADS Livestock Value Estimation Supplementary Notes"
author: PPSTheme
output: 
    pdf_document:
        toc: true
        df_print: kable
vignette: >
  %\VignetteIndexEntry{Documentation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  
bibliography: ../references.bib
csl: "../cambridge-university-press-numeric.csl"
link-citations: true
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE,
  comment = "#>"
)

knitr::opts_knit$set(
  root.dir = here::here(".")
)

suppressPackageStartupMessages({
  library(DiagrammeR) # For the flow diagrams
})
```


```{r}
config <- config::get()

print_table <- function(data, caption) {
  data |>
    knitr::kable(caption = caption) |>
    kableExtra::kable_styling(font_size = 8)
}
```

\newpage

# Calculations 


The following section details the process of obtaining both asset value and 
output value estimates for terrestrial livestock and aquaculture. 



### Livestock 



\newpage

## Asset Value Calculation


The following set of equations outlines the terms and calculations used to
obtain the livestock asset value for a single livestock animal type in a single
country for one year during the observational period.


$$
\begin{aligned}
    \text{Carcass Yield} &= \text{No. Slaughtered (Head)} \times \text{No. Slaughtered (Tonnes)} \\
    \text{Average Live Body Weight}&= \text{Carcass Yield} \times \text{Carcass Percent}^{-1} \\
    \text{Asset Value} &= \text{Price per Tonne} \times \text{Average Live Bodyweight (tonnes)} \times \text{Livestock Population}
\end{aligned}
$$

The following flow chart describes the process of calculating the asset value 
for a single livestock animal type in a single country for one year 
during the observational period. 



```{r, fig.cap="Livestock Asset Value Calculation Flow Diagram"}
mermaid("graph TB;A[Number Livestock Slaughtered]-->C;B[Quanitity Livestock Slaughtered]-->C;C[Tonnes/Head = Carcass Yield] -->E;D[Carcass Percentage]-->E;E[Yield/Carcass Percentage = Average Live Body Weight]-->G;F[Liveweight Price Per Tonne]-->G;G[Liveweight Price Per Tonne/Average Live Body Weight = Price Per Live Animal]-->I;H[Livestock Population]-->I;I[Asset Value];")
```

\newpage

# Codes 

## Aquaculture

The main unit that is used to subset the data is the custom grouping 

> "Fish, crustaceans and molluscs, etc.."

which is what is used in the FAOSTAT yearbook. This subsets the species used to
the main commercial products and excluded production figures for aquatic plants,
pearls and mother-of-pearl. This subsetting and grouping  is outlined in the
Global Aquaculture Production database metadata at `Aqua_E.html`, other notes on
the data are also given in `NOTES_AQUACULTURE_COUNTRY_EN.html`[@FAO2021b].
 
\newpage
 
 
## Crops 

The following table shows the crop codes used [@FAO2021c]. 

```{r}
readRDS(here::here("data", "codes", "faostat", "FAOSTAT_CPC_cropItemCodes.Rds")) |>
  print_table(caption = "FAOSTAT to CPC Crop Codes and Groupings")
```

\newpage





## Value of Production

The following table shows the FAOSTAT Value of Agricultural Production [@FAO2021] 
item codes used. 

- For this paper project only the `Non-Indigenous` value of production items 
were used. 


```{r}
readRDS(
  here::here(config$data$codes$faostat$dir, "FAOSTAT_VOP_Items_NonIndigenous_Codes.rds")
) |>
  print_table(caption = "FAOSTAT Value of Production Livestock Output Item Codes Used")
```


\newpage

## Producer Prices Meat Live Weight

The following table shows the "Meat, live weight <animal>" producer price 
codes used in the FAOSTAT database. 


```{r}
readRDS(here::here(config$data$codes$faostat$dir, "FAOSTAT_Meat_Live_Weight_Codes.rds")) |>
  dplyr::distinct(`Item Code`, .keep_all = TRUE) |>
  print_table(caption = "FAOSTAT Producer Prices Live Weight Item Codes used")
```

\newpage


## FAOSTAT Livestock Items 

The following table displays the Livestock Species item codes which are 
used in this analysis. These codes are used to produce the asset value for each 
species. The number of species may of course differ for each country. 

```{r}
readRDS(
  here::here(config$data$codes$faostat$dir, "FAOSTAT_Livestock_Codes.rds")
) |>
  dplyr::filter(`Domain Code` == "QCL") |>
  dplyr::distinct(Item, .keep_all = TRUE) |>
  print_table(
    caption = "FAOSTAT Production and Livestock Products Livestock (Stock) Item Codes Used"
  )
```




## Country ISO3 Codes 

The following table shows the ISO3 codes for regions which are included in this
analysis, including the years in which the code designation applies.

```{r}

arrow::read_parquet(here::here(config$data$codes$faostat$country_codes$output_codes)) |>
  dplyr::select(country, m49_code, iso3_code, start_year, end_year) |>
  print_table(caption = "ISO3 Country Codes Included in this Analysis")
```

\newpage

## Technical Conversion Factors 

Technical conversion factors for animal body weights are derived directly from
FAOSTAT production data, or using the values given in the in their technical
conversion factors documentation [@faoTechnicalConversionFactors2012].


*Note: There are inconsistencies in how different countries report body weights,
with some reporting only sold animals, and others the average live body weight
of their entire stock. The carcass percentage also varies per animal depending
on what value is included in the output FAOSTAT Commodity tree.*

In the cases where countries have missing values for different livestock types
these values have been imputed using the regional median value for each of the
live body weight, carcass weight and carcass percentage.

The following table shows these a glimpse at these values once they are 


```{r}
arrow::read_parquet(
  here::here(config$data$output$technical_conversion_factors_imputed)
) |>
  dplyr::glimpse()
```




# References
